Xor-Some Preregistered Study: Visualizations

### 2021-10-23 analysis/main/01_xor-some_prereg_preprocessing_N158.Rmd
refactor repo, preprocess N158

First, the data is loaded.
```{r, echo=FALSE}
d <- read_csv("./../data/main/results_73_xor-some-Prolific-main_N18_anonym.csv")

@@

cat(" Mean age: ", d_native %>% pull(age) %>% mean(., na.rm = T) )
d_native  %>% count(gender) %>% mutate(n = n/72)
```

Check the overall completion time. Participants who complete the experiment in less than 8 minutes are excluded.
```{r}
d_native_completed <- d_native %>% mutate(timeSpent = round(timeSpent, 2)) %>%
  filter(timeSpent > 8) 
```

```{r}
# check the distribution of completion times
d_native_completed %>% 
  ggplot(., aes(x=timeSpent)) +
  geom_density()
```

@@

d_native_attended <- left_join(d_native_completed, 
                               d_native_attention_summary, 
                               by = c("submission_id"))

Data frames preparation:
```{r}
d_main <- d_native_attended %>% select(-age, -comments, -education, -endTime, 
                              -gender, -languages, -optionLeft, -optionRight, -startDate,
                              -startTime, -timeSpent, -expected) %>%
  filter(trial_name != "example", trial_name != "attention_check")
d_exmpl <- d_native_attended %>% select(-age, -comments, -education, -endTime, 
                              -gender, -languages, -optionLeft, -optionRight, -startDate,
                              -startTime, -timeSpent, -expected) %>%
  filter(trial_name == "example")
d_critical <- d_main %>% filter(condition == "critical")

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../data/main/results_prereg_raw_N18_test.csv")
```

@@

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../data/main/results_prereg_N18_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../data/main/results_prereg_tidy_N18_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../data/main/results_prereg_tidy_N18_zScored_wide.csv")
```

>>>>

First, the data is loaded.
```{r, echo=FALSE}
d <- read_csv("./../../data/main/results_73_xor-some-Prolific-main_N158_anonym.csv")

@@

cat(" Mean age: ", d_native %>% pull(age) %>% mean(., na.rm = T) )
d_native  %>% count(gender) %>% mutate(n = n/80)
```

Check the overall completion time. Participants who complete the experiment in less than 8 minutes are excluded.
```{r}
d_native_completed <- d_native %>% mutate(timeSpent = round(timeSpent, 2)) %>%
  filter(timeSpent > 8)

cat(" Number of participants who completed the expt in > 8 minutes: ", d_native_completed %>% distinct(submission_id) %>% count() %>% pull() )
```

```{r}
d_native_completed %>% summarize(median_time = median(timeSpent),
                                 mean_time = mean(timeSpent))
```
```{r}
# check the distribution of completion times
d_native_completed %>% 
  ggplot(., aes(x=timeSpent)) +
  geom_density()
```

@@

d_native_attention_failed <- d_native_attention %>% 
  group_by(submission_id) %>%
  summarize(attention_prop = mean(passed_attention_trial)) %>%
  mutate(
    passed_attention_check = attention_prop > 0.75
  ) %>% 
  filter(passed_attention_check == FALSE)

d_native_attended <- anti_join(d_native_completed, 
                               d_native_attention_failed, 
                               by = c("submission_id"))

cat(" Number of participants failing attention checks: ", d_native_attention_failed %>% distinct(submission_id) %>% count() %>% pull() )
```

Data frames preparation:

```{r}
d_main <- d_native_attended %>% select(-age, -comments, -education, -endTime, 
                              -gender, -languages, -optionLeft, -optionRight, -startDate,
                              -startTime, -timeSpent, -expected) %>%
  filter(trial_name != "example", trial_name != "attention_check")
d_exmpl <- d_native_attended %>% select(-age, -comments, -education, -endTime, 
                              -gender, -languages, -optionLeft, -optionRight, -startDate,
                              -startTime, -timeSpent, -expected) %>%
  filter(trial_name == "example")
d_critical <- d_main %>% filter(condition == "critical")

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../../data/main/results_prereg_raw_N158_test.csv")
```

@@

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../../data/main/results_prereg_N158_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_N158_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_N158_zScored_wide.csv")
```

### 2021-10-23 analysis/main/01_xor-some_prereg_preprocessing_N18.Rmd
refactor repo, preprocess N158

First, the data is loaded.
```{r, echo=FALSE}
d <- read_csv("./../../data/main/results_73_xor-some-Prolific-main_N158_anonym.csv")

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../../data/main/results_prereg_raw_N158_test.csv")
```

@@

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../../data/main/results_prereg_N158_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_N158_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_N158_zScored_wide.csv")
```

>>>>

First, the data is loaded.
```{r, echo=FALSE}
d <- read_csv("./../../data/main/results_73_xor-some-Prolific-main_N18_anonym.csv")

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../../data/main/results_prereg_raw_N18_test.csv")
```

@@

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../../data/main/results_prereg_N18_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_N18_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_N18_zScored_wide.csv")
```

### 2021-10-23 analysis/prereg/02_xor-some_prereg_plots.Rmd
refactor repo, preprocess N158

Read data created in preprocessing script:
```{r}
d_critical_zScored_wide <- read_csv("./../../data/results_prereg_tidy_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/results_prereg_tidy_zScored_long.csv")
d_test_raw <- read_csv("./../../results_prereg_raw_test.csv")
```

>>>>

Read data created in preprocessing script:
```{r}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_N18_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_N18_zScored_long.csv")
d_test_raw <- read_csv("./../../data/main/results_prereg_raw_N18_test.csv")
```
